CODECHECK: An Open Science initiative for the independent execution of computations underlying research articles during peer review to improve reproducibility

### 2021-02-24 codecheck-paper.tex
fix

A CODECHECK system, even if temporarily adopted as a sustainable
transition towards more open publication and review practices, can
contribute to increased trust in research outputs. Introducing
CODECHECK should be informed by lessons learned from (introducing)
open peer review \cite{ross-hellauer_guidelines_2019}.  \textbf{Our
conversations with publishers and editors included procedural and
technical implications of openness, be it that open peer review is neither applied
by nor familiar to stakeholders, or that process management software
would not support such open communication. WHAT DOES THIS SENTENCE
MEAN??  JUST DELETE?}

>>>>

A CODECHECK system, even if temporarily adopted as a sustainable
transition towards more open publication and review practices, can
contribute to increased trust in research outputs. Introducing
CODECHECK should be informed by lessons learned from (introducing)
open peer review \cite{ross-hellauer_guidelines_2019}.  Our
conversations with publishers and editors indicate a willingness to
adopt open practices like these, but that it is hard to innovate with
legacy infrastructure and established practices.
